\Title

### 2021-06-28 manuscript/content.tex
Refer to new gb interpolation section in methods
Point to it when we talk about randomizing windows.
Break up the optimization used in EQL GB
Using only data inside the window and forward modelling by summation
were locked inside a large paragraph. Use an enumerate to make it clear
that there are two optimizations and make them jump out in the text a
bit more.

\begin{enumerate}
  \item
    \emph{Sources below data points}: one equivalent source is placed at the
    horizontal location of each data point (Fig.~\ref{fig:source_layouts}b).
    Therefore, the number of sources is equal to the number of observations
    ($M=N$).
  \item
    \emph{Regular grid}: a homogeneous distribution of point sources below the
    survey region (Fig.~\ref{fig:source_layouts}c). A padding region is often
    added to help reduce edge effects. In practice, it often leads to
    underdetermined problems since a large number of sources is required
    ($M>N$).
\end{enumerate}

@@

\begin{enumerate}
    \item Dividing the survey region into rectangular blocks of equal size.
    \item \label{item:median-position} Computing the median horizontal position
        of the observation points that fall inside each block. Blocks without
        any observation point are omitted.
    \item Assign one point source to each of the median horizontal positions
      calculated in step \ref{item:median-position}.
\end{enumerate}

The number of sources created by this new layout will be less than the number
of observations if the block size is chosen appropriately (i.e., making sure
that blocks are large enough to contain more than a single data point).
The overdetermined problem that arises from this layout has a lower
computational load and is less prone to overfitting the data since the model
complexity is lower.
Moreover, the block averaging process can balance the spacing between sources
along a flight line and between adjacent lines, helping to reduce aliasing
effects in the generated grids.
In Section~\ref{sec:synthetic_distributions}, we demonstrate through tests on
synthetic data that the block-averaged sources layout is able to interpolate
with comparable accuracy to other layouts while using a fraction of the
equivalent sources.

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
    \caption{
        Examples of different strategies for assigning depths to equivalent
        sources.
        Here we assign one source for each
        observation point, located at the same horizontal coordinates as the
        data points.
        Source depths are
        (a)~a \emph{constant depth} at a chosen vertical coordinate,
        (b)~a \emph{relative depth} determined by uniformly shifting downward
        the vertical coordinate of data points,
        and
        (c)~a \emph{variable depth} determined by shifting the vertical
        coordinates of the observation points by an amount proportional to the
        average distance to neighbouring sources.
        The distance between data points and their respective sources (a)
        depends on observation height, (b) is constant, and (c) is proportional
        to the horizontal distribution of sources.
        Notice how the closely spaced sources in the middle of the profile (c)
        are shallower than their counterparts in (b).
    }
    \label{fig:depth_types}
\end{figure*}

@@

\noindent
in which $z$ is the vertical coordinate (positive downwards) of an equivalent
source,
$\Delta z$ is a relative depth shift that is the same for all sources,
$\alpha$ is an adimensional depth factor,
$h$ is the median horizontal distance to the $k$ nearest neighbouring sources,
and
$z_{obs}$ is a vertical observation coordinate that will depend on the
horizontal layout strategy.
For \emph{sources below data}, it is the vertical coordinate of the data point
corresponding to the given source.
For \emph{regular grid}, it can be interpolated from the vertical coordinates
of all data points.
Finally, for \emph{block-averaged sources} it will be the median vertical
coordinate of the data within the corresponding block.

In Section~\ref{sec:synthetic_distributions}, we test the effectiveness each of
these strategies on synthetic data.

>>>>

\begin{enumerate}
  \item
    \emph{Sources below data points}: one equivalent source is placed at the
    horizontal location of each data point (Fig.~\ref{fig:source_layouts}b).
    Therefore, the number of sources is be equal to the number of observations
    ($N=M$).
  \item
    \emph{Regular grid}: a homogeneous distribution of point sources below the
    survey region (Fig.~\ref{fig:source_layouts}c). A padding region is often
    added to help reduce edge effects. In practice, it often leads to
    underdetermined problems since a large number of sources is required
    ($N<M$).
\end{enumerate}

@@

\begin{enumerate}
    \item Dividing the survey region into rectangular blocks of equal size.
    \item \label{item:median-position} Computing the median horizontal position
        of the observation points that fall inside each block. Blocks without
        any observation point are omitted.
    \item Assign one point source to the median horizontal position calculated
        in step \ref{item:median-position}.
\end{enumerate}

The number of sources created by this new layout will be less than the number
of observations if the block size is chosen appropriately (i.e., making sure
that blocks are large enough to contain more than a single data point).
The overdetermined problem that arises from this layout has a lower
computational load and is less prone to overfitting the data since the model
complexity is lower.
Moreover, the block averaging process can balance the spacing between sources
along a flight line and between adjacent lines, helping to reduce aliasing
effects in generated grids.
We will demonstrate through tests on synthetic data that the block-averaged sources
layout is able to interpolate with comparable accuracy to other layouts while
using a fraction of the equivalent sources.

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
    \caption{
        Examples of different strategies for assigning depths to equivalent
        sources.
        Here we assign one source for each
        observation point, located at the same horizontal coordinates as the
        data points.
        Source depths are
        (a)~a \emph{constant depth} at a chosen vertical coordinate,
        (b)~a \emph{relative depth} determined by uniformly downward shifting
        the vertical coordinate of data points,
        and
        (c)~a \emph{variable depth} determined by shifting the vertical
        coordinates of the observation points by an amount proportional to the
        average distance to neighbouring sources.
        The distance between data points and their respective sources (a)
        depends on observation height, (b) is constant, and (c) is proportional
        to the horizontal distribution of sources.
        Notice how the closely spaced sources in the middle of the profile (c)
        are shallower than their counterparts in (b).
    }
    \label{fig:depth_types}
\end{figure*}

@@

\noindent
in which $z$ is the depth of an equivalent source,
$\Delta z$ is a relative depth shift that is the same for all sources,
$\alpha$ is an adimensional depth factor,
$h$ is the median horizontal distance to the $k$ nearest neighbouring sources,
and
$z_{obs}$ is a vertical observation coordinate that will depend on the
horizontal layout strategy.
For \emph{sources below data}, it is the vertical coordinate of the data point
corresponding to the given source.
For \emph{regular grid}, it can be interpolated from the vertical coordinates
of all data points.
Finally, for \emph{block-averaged sources} it will be the average vertical
coordinate of data within the corresponding block.

In the following sections, we will test the effectiveness and trade-offs of
each of these strategies on synthetic data.
